% !TEX root = thesis.tex

%% Document Metadata

%% The location of your Assignment Statement (scanned as image)
% \thesisspec{figures/thesisspec.png}

\title{Jira: Komplexný nástroj pre riadenie agilných projektov}{Jira: A Comprehensive Tool for Agile Project Management}
\thesis{Referát}{Technical Report}

\author[Bc.]{Michal}{Jankura}
\secondauthor[Bc.]{Erik}{Rašš}
\supervisor{Ing. Sebastián Hreško}
% \consultant{Donald E. Knuth}
% \consultantsaffiliation{Stanford University}{Stanfordská univerzita}
\college{Technická univerzita v Košiciach}{Technical University of Košice}
\faculty{Fakulta elektrotechniky a informatiky}{Faculty of Electrical Engineering and Informatics}
\department{Katedra počítačov a informatiky}{Department of Computers and Informatics}
\departmentacr{KPI}{DCI}
\submissiondate{25}{2}{2026}
\fieldofstudy{Informatika}
\studyprogramme{Informatika}

\keywords{%
  % english
  Jira, agile methodologies, Scrum, Kanban, project management, software development
}{%
  % slovak
  Jira, agilné metodiky, Scrum, Kanban, projektové riadenie, softvérový vývoj
}



\abstract{%
  % english
  This paper provides a comprehensive analysis of Jira as a leading solution for agile project management in software engineering. The work examines in detail the technical architecture of the system, its key functionalities including task management, agile boards, and reporting tools. Special attention is given to the practical use of Jira in individual phases of the project cycle. The paper also includes a critical evaluation of the tool's advantages and disadvantages along with a comparative analysis of competing solutions.
}{%
  % slovak
  Tento referát sa zaoberá komplexnou analýzou nástroja Jira ako popredného riešenia pre riadenie agilných projektov v~softvérovom inžinierstve. Práca detailne skúma technickú architektúru systému, jeho kľúčové funkcionality vrátane správy úloh, agilných dosiek a~reportingových nástrojov. Osobitná pozornosť je venovaná praktickému využitiu Jiry v~jednotlivých fázach projektového cyklu. Súčasťou práce je aj kritické zhodnotenie výhod a~nevýhod nástroja spolu s~porovnávacou analýzou konkurenčných riešení.
}




% Uncomment the following line for the printer-friendly version of the thesis.
% When defined, final PDF will not contain colored links, which is useful for printing.
% WARNING: Uncomment ONLY when used manually without the Docker image for building the thesis. By uncommenting this line, you will manually override the printable flag and behavior of the Docker image will not work as expected.
% If you want to use the Docker image for building the document, please do not uncomment this line.
%\def\printable{}

